---
title: What are my flatmates eating today? 
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
 body {color:black ;
  background-color:violet}
  
h2 {
        font-family: 'Yusei Magic', sans-serif;
      }
      .shiny-input-container {
        color: #474747;
      }
```

## What are my flatmates eating today?

We did an observational logging about what type of food my flatmates are eating on certain times, and if they used the stove to prepare it. 

This Report shows summaries about the observation.


```{r}
library(tidyverse)
library(ggplot2)
logged_data <- ("https://docs.google.com/spreadsheets/d/e/2PACX-1vQey5iL0YQAWoVC5k3JWdGjTHvunGVXUKPspRW_hLMyteO14R9AE4_IGoDIiFgzbC9YZpHZGBGVy35i/pub?output=csv")
latest_data <- read_csv(logged_data)%>%
  rename(food_type = 2,
         time_ = 3,
         stove_usage = 4,
         cleanliness = 5,
         usage = 6)
```



**The average minutes spent by my flatmates using the stove is**
```{r}
# used to get the  mean of the minutes spent using the stove without the missing values from the second part of the google form
mean(latest_data$usage,na.rm = TRUE)
```


**The least minutes spent by my flatmates using the stove is**
```{r}
#used to get the minimum minutes spent using the stove without the missing values from the second part of the google form
min(latest_data$usage,na.rm=TRUE)

```



**The most minutes spent by my flatmates using the stove is**
```{r}
#used to get the maximum minutes spent using the stove without the missing values from the second part of the google form
max(latest_data$usage,na.rm = TRUE)
```


**This bar chart named as Plot 1 compares the variable time_  with the variable stove_usage**
```{r}

#used to name the chart plot1 that fills time_  with stove_usage, and to make the bar more informative and descriptive
plot1<- latest_data%>%
  ggplot(na.rm=TRUE) +
  geom_bar(aes(x = time_, fill=stove_usage)) +
  labs(title = "What time did my flatmates used the stove the most?",
       subtitle = "Comparing what times my flatmates used the stove to prepare their food",
       x ="Time",
       y = "Number of meals",
       caption = " 
Breakfast - 4:00-10:30
Lunch - 10:30-15:30 
Dinner 15:31-3:59")


plot1 + theme(legend.position = ("bottom"),
              legend.key = element_rect(fill = "red", colour = "black"),
              legend.text = element_text(size = 8, colour = "black"),
              legend.title = element_text(face = "bold"
              ))
```





**This bar chart named as Plot 2 compares the variable food_type  with the variable time_**
```{r}
#used to name the chart plot2 that fills food_type with time_, and to make the bar more informative and descriptive
plot2<- latest_data%>%
  ggplot() +
  geom_bar(aes(x = food_type, fill= time_)) +
  labs(title = "What did my flatmates eat on certain times?",
       subtitle = "Comparing what group of food my flatmates eat between breakfast, lunch, and dinner",
       x ="Food Group",
       y = "Number of meals",
       caption = " 
Breakfast - 4:00-10:30
Lunch - 10:30-15:30 
Dinner 15:31-3:59")

#used to make the plot2 more creative
plot2 + theme(legend.position = ("bottom"),
              legend.key = element_rect(fill = "white", colour = "black"),
              legend.text = element_text(size = 8, colour = "black"),
              legend.title = element_text(face = "bold"))


```




